Prefetching SPARQL query cacher

### 2016-05-25 dissertation/cache-proxy.tex
minor

I decided to set the entire system up as a proxy server, and run a
realistic query against DBpedia repeatedly. The intention was to let
the analyser find all required data and eventually add that to the
cache. Once the cache was filled with all the data, the query cache
should be able to answer the query on its own, at least within a time
period on the order of a magnitude of the original endpoint (which
took ca. 1~second).

@@

The cache was kept in a Redis data structure database on a machine
with a Intel Core2 Duo E8500 CPU with 16 GB of RAM. The proxy server
with the query engine ran on a Intel Xeon CPU E3-1230 v5 CPU with 32
GB of RAM, residing a LAN with a gigabit Ethernet link between
them. Running the query on this query took more than 1000 seconds
without any performance analysis enabled. This is clearly more than
two orders of magnitude longer than acceptable. Moreover, it is then
clearly not possible to draw any conclusions as to whether the system
would be helpful in achieving its goal of taking load off of the
remote server, as it could process far fewer queries than the public
remote endpoint, and any load saved on the remote endpoint would
likely be less than the uncertainty arising from that.

@@

While this design would achieve the goal that a combination of levels
would correspond to the null hypothesis, certain levels are somewhat
problematic. For example, the Linked Data Fragments client in point~2
might be an implementation of \cite{verborgh2014querying}, but that
would be very different from the combination of point~1~and~2, which
correspond to the usage of
\pmodule{AtteanX::QueryPlanner::Cache::LDF}. Additionally, I noted
that downloading the triple pattern fragment \sparql{?s foaf:name
  ?name .}  resulted in more than 40~000 HTTP requests due to
paging. Another relevant factor might be to deploy a Triple Pattern
Fragments server that does not page, and have levels with paging on
and off. Integrating this factor in the experimental design would
further complicate it.

>>>>

I decided to set the entire system up as a proxy server, and run a
realistic query against DBpedia repeatedly. The intention was to let
the analyser find all required data and eventually add that to the
cache. Once the cache was filled with all the data, the query cache
should be able to answer the query on its own, at least within a time
period on the order of a magnitude of the original endpoint (which
took on the order of 1~second).

@@

The cache was kept in a Redis data structure database on a machine
with a Intel Core2 Duo E8500 CPU with 16 GB of RAM. The proxy server
with the query engine ran on a Intel Xeon CPU E3-1230 v5 CPU with 32
GB of RAM, residing a LAN with a gigabit Ethernet link between
them. Running the query on this hardware took more than 1000 seconds
without any performance analysis enabled. This is clearly more than
two orders of magnitude longer than acceptable. Moreover, it is then
clearly not possible to draw any conclusions as to whether the system
would be helpful in achieving its goal of taking load off of the
remote server, as it could process far fewer queries than the public
remote endpoint, and any load saved on the remote endpoint would
likely be less than the uncertainty arising from that.

@@

While this design would achieve the goal that a combination of levels
would correspond to the null hypothesis, certain levels are somewhat
problematic. For example, the Linked Data Fragments client in point~2
might be an implementation of \cite{verborgh2014querying}, but that
would be very different from the combination of point~1~and~2, which
correspond to the usage of
\pmodule{AtteanX::QueryPlanner::Cache::LDF}. Additionally, I noted
that downloading the triple pattern fragment
\sparql{?s~foaf:name~?name~.}  
resulted in more than 40~000 HTTP requests due to
paging. Another relevant factor might be to deploy a Triple Pattern
Fragments server that does not page, and have levels with paging on
and off. Integrating this factor in the experimental design would
further complicate it.
